### 2012-12-24 inst/examples/sensitivity.Rmd
update plotting routines to compare against true (RickerAllee), alt (Ricker), and est (RickerAllee)

```{r}

@@

```{r }
seed <- round(runif(32) * 1e6)
seed[1] <- 1
seed
yields <- lapply(seed, 
function(seed_i){
  Xo <- allee + x_grid[10] # observations start from
  x0 <- Xo # simulation under policy starts from
  obs <- sim_obs(Xo, z_g, f, p, Tobs=40, seed = seed_i)
  alt <- par_est(obs)
  est <- par_est_allee(obs, f, p)
  gp <- bgp(X=obs$x, XX=x_grid, Z=obs$y, verb=0,
          meanfn="constant", bprior="b0", BTE=c(2000,16000,2),
          m0r1=FALSE, corr="exp", trace=FALSE, 
          beta = beta, s2.p = s2.p, d.p = d.p, nug.p = nug.p, tau2.p = tau2.p,
          s2.lam = "fixed", d.lam = "fixed", nug.lam = "fixed", tau2.lam = "fixed")      
  gp_plot(gp, f, p, est$f_alt, est$p_alt, x_grid, obs, seed_i)
#  posteriors_plot(gp, priors) # needs trace=TRUE!
  OPT <- optimal_policy(gp, f, est$f_alt, alt$f_alt,
                        p, est$p_alt, alt$p_alt,
                        x_grid, h_grid, sigma_g, 
                        est$sigma_g_alt, alt$sigma_g_alt, 
                        delta, xT, profit, reward, OptTime)
  dt <- simulate_opt(OPT, f, p, x_grid, h_grid, x0, z_g, profit)
  sim_plots(dt, seed=seed_i)
  profits_stats(dt)
})
```

>>>>

@@

```{r }
seed <- round(runif(2) * 1e6)
seed[1] <- 1
seed
yields <- lapply(seed, 
function(seed_i){
  Xo <- allee + x_grid[10] # observations start from
  x0 <- Xo # simulation under policy starts from
  obs <- sim_obs(Xo, z_g, f, p, Tobs=40, seed = seed_i)
  alt <- par_est(obs)
  est <- par_est_allee(obs, f, p)
  gp <- bgp(X=obs$x, XX=x_grid, Z=obs$y, verb=0,
          meanfn="constant", bprior="b0", BTE=c(2000,16000,2),
          m0r1=FALSE, corr="exp", trace=FALSE, 
          beta = beta, s2.p = s2.p, d.p = d.p, nug.p = nug.p, tau2.p = tau2.p,
          s2.lam = "fixed", d.lam = "fixed", nug.lam = "fixed", tau2.lam = "fixed")      
  gp_plot(gp, f, p, est$f, est$p, alt$f, alt$p, x_grid, obs, seed_i)
#  posteriors_plot(gp, priors) # needs trace=TRUE!
  OPT <- optimal_policy(gp, f, est$f, alt$f,
                        p, est$p, alt$p,
                        x_grid, h_grid, sigma_g, 
                        est$sigma_g, alt$sigma_g, 
                        delta, xT, profit, reward, OptTime)
  plot_policies(x_grid, OPT$gp_D, OPT$est_D, opt$true_D, opt$alt_D)
  dt <- simulate_opt(OPT, f, p, x_grid, h_grid, x0, z_g, profit)
  sim_plots(dt, seed=seed_i)
  profits_stats(dt)
})
```
